---
title: "R Notebook"
output: html_notebook
---
2017-09-09<br></br>
该例子是来自于(https://zhuanlan.zhihu.com/p/29126173?group_id=889051416948244480)
<img src = "fig1.png">
<h2>图形绘制思路</h2>
<ol>
<li>先绘制柱状图</li>
<li>修改颜色、主题和辅助线等</li>
<li>极坐标转换</li>
<li>文字和图例</li>
</ol>
<hr>
<center><h3>导入包</h3></center>
```{r}
library(ggplot2)
library(showtext)
library(grid)
library(Cairo)
```
<center><h3>构建数据，绘制柱状图</h3></center>
```{r}
mydata <- data.frame(
  id = 1:13,
  class = rep_len(1:4, length = 13),
  Label = c("events", "lead list", "partner", "marketing & advertising",
            "tradeshows", "paid search", "webinar", "emial campaign",
            "sales generator", "website", "other", "facebook/twitter/other",
            "employee & customer referrals"),
  Value = c(7.6, 15.5, 17.9, 21.8, 29.6, 29.7, 32.7, 43.0, 57.5, 61.4, 67.4, 68.6, 68.7)
)
p <- ggplot()
p1 <- p + geom_col(data = mydata, aes(x = id, y = Value, fill = factor(class)), colour = NA, width = 1)
p1
```
假设此处<b>直接</b>极坐标转换，结果是：
```{r}
p2 <- p1 + coord_polar()
p2
```
所以，我们需要对柱状图进行调整，我们需要将每个柱的中心点在一条水平线，这样在极坐标转换后，中心在同一条曲线上，如最上面的图那样！
```{r}
p3 <- p + geom_col(data = mydata, aes(x = id, y = Value/2+100, fill = factor(class)), colour = NA, width = 1)
p3
#将下半部遮盖
p4 <- p3 + geom_col(data = mydata, aes(x = id, y = 100-Value/2), fill = "white", width = 1, colour = "white")
p4
```
现在尝试极坐标转换，发现还是有问题，原图只占据了园周长的一半，对应的方法就是使得整个图的宽度占X轴的一半
```{r}
p4 + coord_polar(theta = "x", direction = 1, start = -14.275)
p5 <- p4 + scale_x_continuous(limits = c(0,26), expand = c(0,0))
p5
```
<b>添加辅助线</b>
```{r}
p6 <- p5 + geom_line(data = NULL, aes(x=rep(c(0.5, 13.5), 2), y = rep(c(76, 124), each = 2), group = factor(rep(1:2, each=2))), linetype = 2, size = 0.25)
p6
```
<b>添加label</b>，前11个较高， 后两个位置稍低
```{r}
p7 <- p6 + geom_text(data = mydata, aes(x = id, y = ifelse(id<11, 160, 125), label = Label),size = 1.5, hjust = 0.5)  ##
p7 
p8 <- p7 + geom_text(data = mydata, aes(x = id, y = ifelse(id<11, 185, 150), label = paste0(Value, "%"), hjust = 0.5, size = 2.5))
p8
```
<center><h3>极坐标转换</h3></center>
```{r}
p9 <- p8 + coord_polar(theta = "x", start = -14.275, direction = 1) + theme_void()
p9
```
<center><h3>文字图例、精修图表</h3></center>
```{r}
##标题与副标题
title = "Events,Lead Lists and partners-\nmore likely be colosed-lost"
content="Marketing events may by fun, but they create\nlousy sales opprunities.When analyzing share\nof closed-won vs.closed-lost opportunities,\nevents,leads lists and partners seem to provide the\nworst performance,while refreals and social\nprovide the best performance."
CairoPNG(file = "polar_bar.png", width = 1200, height = 900)
showtext.begin()
grid.newpage()
pushViewport(viewport(layout = grid.layout(6, 8 )))
vplayout <- function(x, y){viewport(layout.pos.row = x, layout.pos.col = y)}
print(p9, vp = vplayout(1:6, 1:8))
grid.text(label = title, x = 0.5, y = 0.6525, gp = gpar(col = "black", fontsize = 15, draw = TRUE, just = "left", fontface = "bold"))
grid.text(label = content, x=0.5, y = 0.56, gp = gpar(col = "black", fontsize = 12, draw = TRUE, just = "left"))
showtext.end()
dev.off()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
